Robust Bayesian Analysis of Causal Inference in Medical Diagnosis and Treatment

### 2024-07-31 JASA-template.tex
Fix.

\added{%
Unfortunately, without fully controlled randomised trials and full
knowledge of potential confounders, it is well understood that
statistical models are unable to infer causality, as correlation
does not imply causation especially in the presence of confounders.
Still, it is highly desirable to try to adjust for confounding in
our statistical models to the best of our ability. This is termed
(perhaps somewhat unfortunately) \emph{causal inference} in the
literature
\citep{rubin1978,rosenbaum83,Robins1986ANA,winship99,stuart10,Zigler2014,wang2015,koch2018,Hahn2018,koch2020}.
This is also the approach that we will follow here, under the
disclaimer that whether actual causality can be inferred
remains a subject of interpretation and conjecture specific to the
sitation being studied.%
}

>>>>

\added{%
Unfortunately, without fully controlled randomised trials and full
knowledge of confounders, it is well understood that
statistical models are unable to infer causality, as correlation
does not imply causation especially in the presence of confounders.
Still, it is highly desirable to try to adjust for confounding in
our statistical models to the best of our ability. This is termed
(perhaps somewhat unfortunately) \emph{causal inference} in the
literature
\citep{rubin1978,rosenbaum83,Robins1986ANA,winship99,stuart10,Zigler2014,wang2015,koch2018,Hahn2018,koch2020}.
This is also the approach that we will follow here, under the
disclaimer that whether actual causality can be inferred
remains a subject of interpretation and conjecture specific to the
sitation being studied.%
}
